---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# countNAs

<!-- badges: start -->
<!-- badges: end -->

This package counts the missing values in a data set which grouped by one variable.

## Installation

You can install the development version of countNAs from [GitHub](https://github.com/) with:

```{r}
# install.packages("devtools")
devtools::install_github("stat545ubc-2023/assignment-b2-ZoeZHH/countNAs")
```

## Example
These are basic examples which show you how to solve common problems by using countNAs function:

Example - Applying to an existing dataset, this example computes the number of missing values in the `airquality` dataset grouped by the `cyl` column. 
```{r}
# load your function
library(countNAs)
# load your dataset
library(palmerpenguins)
# apply your function
count_all_missing_by_group(airquality, Month)
```
An alternative way of invoking the `count_all_missing_by_group()`: piping the dataset into the function.
```{r} 
airquality |> count_all_missing_by_group(Month) 
```
The optional `.groups` argument allows us to keep the output grouped by the grouping column. See example below; notice how the output is a grouped tibble, rather than the ungrouped tibble output of the earlier examples. 
```{r} 
count_all_missing_by_group(airquality, Month, .groups = "keep")
```
