---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# countNAs

<!-- badges: start -->
<!-- badges: end -->

The goal of countNAs is to make a function to count missing values for all columns by group

## Installation

You can install the development version of countNAs from [GitHub](https://github.com/) with:

```{r}
# install.packages("devtools")
devtools::install_github("stat545ubc-2023/assignment-b2-ZoeZHH")
```

## Example
These are basic examples which show you how to solve common problems by using countNAs function:

Example 1 - creating your own dataset and apply the countNAs function.
```{r example}
# Creating dataset
small_tbl <- tribble(~group, ~var1, ~var2,
                       "A", 1, NA,
                       "A", 2, "x",
                       "B", NA, "y",
                       "C", 3, "z")
# load your function
library(countNAs)
# Apply the function
count_all_missing_by_group(small_tbl, group)
```
Example 2 - Applying to an existing dataset, this example computes the number of missing values in the `airquality` dataset grouped by the `cyl` column. 
```{r}
# load your function
library(countNAs)
# load your dataset
library(palmerpenguins)
# apply your function
count_all_missing_by_group(airquality, Month)
```
An alternative way of invoking the `count_all_missing_by_group()`: piping the dataset into the function.
```{r} 
airquality |> count_all_missing_by_group(Month) 
```
The optional `.groups` argument allows us to keep the output grouped by the grouping column. See example below; notice how the output is a grouped tibble, rather than the ungrouped tibble output of the earlier examples. 
```{r} 
count_all_missing_by_group(airquality, Month, .groups = "keep")
```
